High-Throughput Computing on High-Performance Platforms: A Case Study

### 2017-09-10 paper.tex
fixing  title, comments at start.

\title{Converging High-Throughput and High-Performance Computing: A Case Study}

@@

\ifreview
General comments to address:
\begin{itemize}
    \color{red} 
    % \item REVIEWER 1: There is a problem with capitalization in some
    % reference titles, ie. [2], [3], [4], [7], [8], [9], [10], [11], [12],
    % [13]. Reference [6] is just an author list, year and title. Should there
    % be more here?\mtnote{Fixed.}
    \item REVIEWER 2:  Key concepts such as pilot jobs, tasks and workloads
    are not meaningfully defined.
    \item REVIEWER 2: the information provided is insufficient to asses in
    how far any of the presented evaluation, characterization or lessons are
    applicable outside of TITAN and PanDA Broker combined.
    \item REVIEWER 2: Several references are of poor quality. For example,
    [19] is a slide collection even though there are many papers for the
    referenced work.\mtnote{Reference [19] is a technical paper.}
    \item REVIEWER 3: Title looks too general for what amounts to the
    implementation of an adapter component in a system that is very specific
    to a single HEP experiment. (In general, title, abstract and conclusions
    seem to over-state the contributions of this paper, considering this is a
    general eScience conference and not a WLCG-specific one.)
\end{itemize}
\fi

>>>>

\title{High-Throughput Computing on High-Performance Platforms: A Case Study}

%\title{Converging High-Throughput and High-Performance Computing: A Case Study}

@@

\ifreview
General comments to address:
\begin{itemize}
    \color{red} 
    % \item REVIEWER 1: There is a problem with capitalization in some
    % reference titles, ie. [2], [3], [4], [7], [8], [9], [10], [11], [12],
    % [13]. Reference [6] is just an author list, year and title. Should there
    % be more here?\mtnote{Fixed.}
    \item REVIEWER 2:  Key concepts such as pilot jobs, tasks and workloads
    are not meaningfully defined.
    % \item REVIEWER 2: the information provided is insufficient to asses in
    % how far any of the presented evaluation, characterization or lessons are
    % applicable outside of TITAN and PanDA Broker combined.
    % \item REVIEWER 2: Several references are of poor quality. For example,
    % [19] is a slide collection even though there are many papers for the
    % referenced work.\mtnote{Reference [19] is a technical paper.}
    % \item REVIEWER 3: Title looks too general for what amounts to the
    % implementation of an adapter component in a system that is very specific
    % to a single HEP experiment. (In general, title, abstract and conclusions
    % seem to over-state the contributions of this paper, considering this is a
    % general eScience conference and not a WLCG-specific one.)
\end{itemize}
\fi
